Paper Figs

### 2023-05-31 graphs_newt_snakes/Paper_figs.Rmd
I adding a new plot

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(gridtext)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library(kableExtra)
library(reshape2)
library(ggplot2)
library(ggpubr)
library(stringr)
library(patchwork)
```

@@

plot <-   ggplot(file_long) +
  ggtitle(title, subtitle = subt)+
  xlab(x_label) + ylab(y_label)+
geom_boxplot(aes(x=factor(sim), y=as.numeric(value), fill=factor(name), alpha = rect_type_a))+ #, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")
  #geom_rect(aes(xmin = as.numeric(xmin), xmax = as.numeric(xmax), ymin = -Inf, ymax = Inf, fill = rect_type)) +
  #scale_fill_manual( values =c("darkred", "steelblue", "white","aliceblue" ), breaks = c('newt_pheno_change', 'snake_pheno_change', "True", "False"),  labels = c('Newt', 'Snake', "True", "False"))+ #labels=c("False",'Newt', 'Snake', "True")
  scale_fill_manual( values = c("darkred", "steelblue" ), breaks = c('newt_pheno_change', 'snake_pheno_change'),  labels = c('Newt', 'Snake'))+
      #geom_boxplot(aes(x=factor(sim, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")), y=as.numeric(value), fill=factor(name)),show.legend = FALSE)+
     theme(plot.title = element_text(size=5)) +
  scale_alpha(guide = 'none')+
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))

@@

file$coevo_speed[file$sim %in% choices[1]] = "Fast Coevolution"
file$coevo_speed[file$sim %in% choices[2]] = "Slow Coevolution"
file$coevo_speed[file$sim %in% choices[3]] = "No Coevolution"
file$coevo_speed = factor(file$coevo_speed, levels=c("Fast Coevolution", "Slow Coevolution", "No Coevolution"))
plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==0),]) +
    facet_wrap(~coevo_speed, ncol=1)+
    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
    geom_line(aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno"),)+#group=rep
    geom_line(aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno"))+#group=rep
    #ylim(-1.,2.5)+
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Species",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8),
                      title =element_text(size=8, face='bold'))
  return(plot)

@@

title = "Phenotype Change Coevolution FLat Map"
boxplot_coevo_slope_flat_map(file3, title, subt, x_label, y_label)

@@

file= GA1_lit
choices=c("K", "F", "E")
min_gen=100
max_gen=50000
title="Different Speeds of Coevolution" 
subt="" 
x_label= "Generations"
y_label= "Phenotype"
fast_slow_no_coevolution(file, choices, min_gen, max_gen, title, subt, x_label, y_label)
```

>>>>

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(gridtext)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library(kableExtra)
library(reshape2)
library(ggplot2)
library(ggpubr)
library(stringr)
library(patchwork)
library(RColorBrewer)
```

@@

plot <-   ggplot(file_long) +
  ggtitle(title, subtitle = subt)+
  xlab(x_label) + ylab(y_label)+
geom_boxplot(aes(x=factor(sim, level=c("A", "B", "E", "C", "I", "D", "M", "F", "G", "J", "H", "N", "K", "L", "O", "P")), y=as.numeric(value), fill=factor(name), alpha = rect_type_a))+ #, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")
  #geom_rect(aes(xmin = as.numeric(xmin), xmax = as.numeric(xmax), ymin = -Inf, ymax = Inf, fill = rect_type)) +
  #scale_fill_manual( values =c("darkred", "steelblue", "white","aliceblue" ), breaks = c('newt_pheno_change', 'snake_pheno_change', "True", "False"),  labels = c('Newt', 'Snake', "True", "False"))+ #labels=c("False",'Newt', 'Snake', "True")
  scale_fill_manual( values = c("darkred", "steelblue" ), breaks = c('newt_pheno_change', 'snake_pheno_change'),  labels = c('Newt', 'Snake'))+
      #geom_boxplot(aes(x=factor(sim, level=c("D", "C", "B", "H", "G", "L", "A", "F", "K", "P", "E", "J", "I", "O", "N", "M")), y=as.numeric(value), fill=factor(name)),show.legend = FALSE)+
     theme(plot.title = element_text(size=5)) +
  scale_alpha(guide = 'none')+
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18), 
                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))

both_coevo_slope_flat_map <- function(file, title, subt, x_label, y_label){

file$snake_GA <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
file$newt_GA <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
file$newt_pheno_change=file$N_pheno_end - file$N_pheno_start
file$snake_pheno_change=file$S_pheno_end - file$S_pheno_start
#file$newt_coevo_slope = (file$N_pheno_end - file$N_pheno_start)/ (file$N_end_gen - file$N_str_gen)
#file$snake_coevo_slope = (file$S_pheno_end - file$S_pheno_start)/ (file$S_end_gen - file$S_str_gen)

#file_long <- tidyr::pivot_longer(file, c(newt_pheno_change, snake_pheno_change))
cols <- brewer.pal(11, "RdBu")
fornewt <- cols[1:4]
forsnake <- cols[8:11]

plot1 <-   ggplot(file) +
  labs(subtitle = "Snake")+
  geom_boxplot(aes(x=factor(snake_GA), y=snake_pheno_change, fill=newt_GA))+
  ylab(y_label) + 
  xlab("Snake GA")+
  ylim(0,6)+
 scale_x_discrete(labels=c("1e-08_0.005" = "GA 1", "1e-09_0.05" = "GA 2", "1e-10_0.5" = "GA 3",
                             "1e-11_5" = "GA 4"))+
     theme(plot.title = element_text(size=5)) +
  #scale_fill_discrete(fornewt, labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
  scale_fill_manual(values = rev(fornewt), labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
   #scale_fill_brewer(fornewt , labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
  #scale_alpha(guide = 'none')+
    #labs(fill = " ")+
  guides(fill=guide_legend(title="Newt GA"))+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18), 
                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))

plot2 <-   ggplot(file) +
 labs(subtitle = "Newt")+
  geom_boxplot(aes(x=factor(newt_GA), y=newt_pheno_change, fill=snake_GA))+
  ylab(" ")+ 
  xlab("Newt GA")+
  ylim(0,6)+
 scale_x_discrete(labels=c("1e-08_0.005" = "GA 1", "1e-09_0.05" = "GA 2", "1e-10_0.5" = "GA 3",
                             "1e-11_5" = "GA 4"))+
     theme(plot.title = element_text(size=5)) +
  #scale_fill_discrete(labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
  #scale_fill_brewer(forsnake)+
  scale_fill_manual(values = forsnake, labels=c('GA 1', 'GA 2', 'GA 3', 'GA 4'))+
  #scale_alpha(guide = 'none')+
    #labs(fill = " ")+
  guides(fill=guide_legend(title="Snake GA"))+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18), 
                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))

leg <- get_legend(plot1)
legp1 <- as_ggplot(leg)
leg2 <- get_legend(plot2)
legp2 <- as_ggplot(leg2)

myplot = ggarrange(plot1+theme(legend.position = "none"), (plot2+theme(legend.position = "none")), arrangeGrob(legp1, legp2, nrow = 2), ncol = 3) + plot_annotation(title = title) & theme(title = element_text( size=18,face = 'bold')) #top=grid::textGrob("title"))

  return(myplot)
}

newt_coevo_slope_flat_map <- function(file, title, subt, x_label, y_label){

file$snake_GA <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
file$newt_GA <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
file$newt_pheno_change=file$N_pheno_end - file$N_pheno_start
#file$snake_pheno_change=file$S_pheno_end - file$S_pheno_start
#file$newt_coevo_slope = (file$N_pheno_end - file$N_pheno_start)/ (file$N_end_gen - file$N_str_gen)
#file$snake_coevo_slope = (file$S_pheno_end - file$S_pheno_start)/ (file$S_end_gen - file$S_str_gen)

#file_long <- tidyr::pivot_longer(file, c(newt_pheno_change, snake_pheno_change))

plot <-   ggplot(file) +
  ggtitle(title, subtitle = subt)+
  geom_boxplot(aes(x=factor(newt_GA), y=newt_pheno_change, fill=snake_GA))+
  xlab(x_label) + ylab(y_label)+

     theme(plot.title = element_text(size=5)) +
  #scale_alpha(guide = 'none')+
    #labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18), 
                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))

@@

file$coevo_speed[file$sim %in% choices[1]] = "Fast Coevolution"
file$coevo_speed[file$sim %in% choices[2]] = "Slow Coevolution"
file$coevo_speed[file$sim %in% choices[3]] = "No Coevolution"
file$coevo_speed = factor(file$coevo_speed, levels=c("Fast Coevolution", "Slow Coevolution", "No Coevolution"))
plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==0),]) +
    facet_wrap(~coevo_speed, ncol=1)+
    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
    geom_line(aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno"),)+#group=rep
    geom_line(aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno"))+#group=rep
    #ylim(-1.,2.5)+
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Species",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18),
                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
  return(plot)

@@

title = "Phenotype Change Coevolution FLat Map"
boxplot_coevo_slope_flat_map(file3, title, subt, x_label, y_label) #coevo_boxplot =
#ggsave("coevo_boxplot.png", plot=coevo_boxplot, height=10, width=15, units=c("in"), dpi=600)

@@

title = "Phenotype Change vs Snake GA, FLat Map"
y_label= "Phenotype Change"
x_label = "Snake GA"
both_coevo_slope_flat_map(file3, title, subt, x_label, y_label)

file= GA1_lit
choices=c("K", "F", "E")
min_gen=100
max_gen=50000
title="Different Speeds of Coevolution" 
subt="" 
x_label= "Generations"
y_label= "Phenotype"
#png("image.png", width = 1600, height = 1200)
p1=fast_slow_no_coevolution(file, choices, min_gen, max_gen, title, subt, x_label, y_label)
ggsave("three_speeds_of_coevolution.png", plot=p1, height=10, width=10, units=c("in"), dpi=600)

#dev.off()
```
